DP problems of interest

### 2012-09-28 docs/roadmap/problems.tex
Nits in problems.

\title{DP problems of interest}
\author{Manohar, Thierry}
\date{}
\begin{document}
\maketitle
\pagestyle{headings}

@@

\subsection{Simplifications}
In some special case, it is possible to transform a non-serial problem into a serial problem, if we can embed the non-serial term into an additional aggregation matrix. For example, we can transform
	\[M_{(i,j)}=\max\left\{\begin{array}{l} \max\limits_{k<i} M_{(k,j)}
	\\ \sum\limits_{k<i, l<j}M_{(k,l)} \end{array}\right.
	\implies M_{(i,j)}=\max\left\{\begin{array}{l} C_{(k,j)} \\ A_{(i-1,j-1)} \end{array}\right.\]
Where $C$ is a matrix that stores the maximum along the column and $A$ is a matrix that stores the sum of the array of the previous elements. They can be easily computed with the additional recurrence.
	\[\begin{array}{rcl} C_{(i,j)}&=&\max(C_{(i-1,j)}, M_{(i,j)}) \\
	A_{(i,j)}&=&A_{(i-1,j)}+A_{(i,j-1)}-A_{(i-1,j-1)}+M_{(i,j)}\end{array}\]

@@

@@

% ----------------------------------------------
\subsection{Smith-Waterman}
Problem: matching two strings $S$, $T$.

@@

% ----------------------------------------------
\subsection{Smith-Waterman with gap extension at different cost}
Problem: matching two strings $S$, $T$.

>>>>

\title{DP problems of interest}
\author{Manohar Jonnalagedda, Thierry Coppey}
\date{}
\begin{document}
\maketitle
\pagestyle{headings}

@@

\subsection{Simplifications}
\subsubsection{Calculus}
In some special case, it is possible to transform a non-serial problem into a serial problem, if we can embed the non-serial term into an additional aggregation matrix. For example, we can transform
	\[M_{(i,j)}=\max\left\{\begin{array}{l} \max\limits_{k<i} M_{(k,j)}
	\\ \sum\limits_{k<i, l<j}M_{(k,l)} \end{array}\right.
	\implies M_{(i,j)}=\max\left\{\begin{array}{l} C_{(k,j)} \\ A_{(i-1,j-1)} \end{array}\right.\]
Where $C$ is a matrix that stores the maximum along the column and $A$ is a matrix that stores the sum of the array of the previous elements. They can be easily computed with the additional recurrence.
	\[\begin{array}{rcl} C_{(i,j)}&=&\max(C_{(i-1,j)}, M_{(i,j)}) \\
	A_{(i,j)}&=&A_{(i-1,j)}+A_{(i,j-1)}-A_{(i-1,j-1)}+M_{(i,j)}\end{array}\]

@@

\subsubsection{Precomputations}
When a calculus computation is impossible, it might be worth to interleave a computation phase that will aggregate some of the results that are necessary to the computation block. For instance, for Nussinov's $\max_{i<k<j} [ M_{(i,k)}+M_{(k+1,j)} ]$ we can precompute it for all rows and columns of the block, and for all elements that are not part of the block, and pass these partial results together at the block launch.

On GPU, this could be done by interleaving a new kernel for this specific purpose, on FPGA, this could be done by preparing the maximums in another memory area whose pointer will later be passed to the co-processor.

@@

% ----------------------------------------------
\subsection{Smith-Waterman (simple)}
Problem: matching two strings $S$, $T$.

@@

% ----------------------------------------------
\subsection{Smith-Waterman (with gap extension at different cost)}
Problem: matching two strings $S$, $T$.
